The Astropy Project

### 2017-11-20 main.tex

The \package{astropy.io.fits} subpackage started as a direct port of the
PyFITS project. Therefore it is pretty stable, with mostly bug fixes but also
a few new features and performance improvements.  The API remains compatible
with PyFITS, which is now deprecated in favor of Astropy.

@@

FITS files are now loaded \emph{lazily} (the default behavior, which can be
deactivated if needed), where all HDUs are not loaded until they are requested
(or the file is closed). This should provide substantial speedups for
situations using the convenience functions (e.g., \texttt{getheader()} or
\texttt{getdata()}) to get HDU’s that are near the front of a file with many
HDUs.

>>>>

The \package{astropy.io.fits} subpackage started as a direct port of the
PyFITS project \citep{PyFITS}. Therefore it is pretty stable, with mostly bug
fixes but also a few new features and performance improvements.  The API
remains compatible with PyFITS, which is now deprecated in favor of
\astropypkg.

@@

FITS files are now loaded \emph{lazily} (the default behavior, which can be
deactivated if needed), where all HDUs are not loaded until they are
requested. This should provide substantial speedups for situations using the
convenience functions (e.g., \texttt{getheader()} or \texttt{getdata()}) to
get HDU’s that are near the front of a file with many HDUs.
